---
title: "Alcohol vs Seat choice"
author: "iboni archie"
date: "summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

It appears that there is a difference between people who choose to sit in the     
back of the class.    

 
```{r}
boxplot(alcohol~Seat,data=davisdata)
```

In this graph it is showing that the people who sit in the back of the class     
drink more alcohol at 30 than the people who choose to sit in the front between   0 and 10 or the middle.    
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

In this plot we see that there are red dots that represent outliers this is       showing that the people who sit in the back are drinking a larger amount of     alcohol in the 45 to 50 range compared to the front seat that is drinking   
between 10 to 20.    

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```
 


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```


It appears that the average number of drinks in the back row is 9.6 and that     
front row's average is 1.8 while the middle row is at 3.28 which is 3x lower     
than the back row    




## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

We will reject the null hypothesis, we will seek more clarification.  


```{r}
plot(TukeyHSD(model1))
```


It appears that there is a diffference between the middle and back rows and the   front and the back rows there is not much difference between the front and the  
middle.  

## Conclusions


